---
title: "Submitting Assignments in MQIM 6604"
author: "Jon Spinney"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Assignments in MQIM 6604 should be completed submitted in Rmarkdown. Rmarkdown is an interactive document that combines text and executable R code in a format that facilitates *reproducible research*. R code is added to the documents in *chunks*, either *inline* (within a line of text) or as a separate code block. An inline code chunk would look like 

```{r, results='asis', echo=FALSE}
cat("`` `r 2+2` ``")
```

and when the document is compiled, the code ("2+2" in this case) would be executed, and the answer `r 2+2` would show inline in the block of text.

Code that is included in a separate chunk will (when rendered into HTML) look like:

```{r,eval=FALSE}
library(quantmod,quietly=TRUE)
getSymbols("^GSPC")
head(GSPC)
```

This code chunk will produce:

```{r,message=FALSE,warning=FALSE}
library(quantmod,quietly=TRUE)
getSymbols("^GSPC")
head(GSPC)
```

Please read through a simple introduction to Rmarkdown such as https://rmarkdown.rstudio.com/articles_intro.html.

Note that it is almost always easier to use the tag "output: html_document" while working on an assignment, as compiling directly to pdf can be a bit of a hassle when considering placement of figures of tables. My recommendation is to always use the "output: html_document" tag in Rstudio/Rmarkdown, and if you want PDF output, do this at the end with the "output: pdf_document" or by printing to PDF later. You will need  \LaTeX installed on your system to use "output: pdf_document".

## Assignment Template

- Assignments must be completed in Rmarkdown.
- Should be clearly labelled as to who contributed to the assignment in the "author:" tag.
- R code is to be included in the document via *knitr chunks* and the live document must be able to be executed/compiled into HTML to produce the assignment output.
- Assignments will be graded on the solutions produced yby the Rmarkdown document as well as the clarity of formatting and the quality of the R code.

Assignments should separate questions with "##" headings, such as:

## Question 1

Use the package **quantmod** to download historical daily prices on the S&P 500 from Yahoo!Finance with the *getSymbols()* function. Plot the Adjusted Close.

```{r}
library(quantmod)
getSymbols("^GSPC")
chart_Series(GSPC)
```

