---
title: "The mqim6604 R Package"
author: "Jon Spinney"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

TBC

## Usage

TBC

## Installing and Loading the Package

Install the package via the **devtools** *install_github()* function:

```{r,eval=FALSE}
# if devtools not installed
#install.packages("devtools")
#library(devtools)
install_github("jspinney-nbimc/mqim6604")
```

Load the package with

```{r,eval=FALSE}
library(mqim6604)
```

## Data Included in the Package

### CDN_LC_STOCKS_RETURN_DATA

This data set contains historical daily total returns on a set of 50 randomly selected Canadian stocks from 2015-01-02 to 2018-02-28.

### CDN_LC_STOCKS_DESC_DATA

Matched with the CDN_LC_STOCKS_RETURN_DATA dataset, this dataset provides descriptive data (sector, market capitalization, etc.) on a set of 50 randomly selected Canadian stocks as of Feb 28, 2018.

## Functions

```{r,eval=FALSE}
EstimateHedge( target_var , hedge_vars)
```

```{r,eval=FALSE}
GetHistoricalPricesYahoo()
```

```{rm eval=FALSE}
Newton()
```

```{r, eval=FALSE}
RandPorts()
```

```{r, eval=FALSE}
SolveRiskParity()
```

## Acknowledgments

TBC

## Legal

All code of the mqim6604 package is licensed under the MIT license.

All data included in the package is either sourced from publicly available locations or provided with permission by  the data owner.
